### 2023-03-16 paper/icse24/tables/test-results-hs-table.tex
icse24

\resizebox{0.7\textwidth}{!}{

@@

\multirow{2}{*}{\parbox{8cm}{LC1: \UseMacro{test-results-hs-lc6}}}

@@

\multirow{2}{*}{\parbox{8cm}{LC2: \UseMacro{test-results-hs-lc7}}}

@@

\multirow{2}{*}{\parbox{8cm}{LC3: \UseMacro{test-results-hs-lc8}}}

@@

\multirow{2}{*}{\parbox{8cm}{LC4: \UseMacro{test-results-hs-lc9}}}

@@

\multirow{2}{*}{\parbox{8cm}{LC5: \UseMacro{test-results-hs-lc10}}}

@@

\multirow{2}{*}{\parbox{8cm}{LC6: \UseMacro{test-results-hs-lc11}}}

@@

\multirow{2}{*}{\parbox{8cm}{LC7: \UseMacro{test-results-hs-lc12}}}

@@

\multirow{2}{*}{\parbox{8cm}{LC8: \UseMacro{test-results-hs-lc13}}}

@@

\multirow{2}{*}{\parbox{8cm}{LC9: \UseMacro{test-results-hs-lc14}}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc14-num-tcs}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc14-num-seeds}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc14-num-exps}}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc14-num-all-fail}/\UseMacro{test-results-hs-bl-model0-lc14-num-fail}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc14-num-all-failrate}/\UseMacro{test-results-hs-bl-model0-lc14-num-failrate}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc14-num-pass-to-fail}\\
 & & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc14-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc14-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc14-num-all-failrate}/\UseMacro{test-results-hs-bl-model1-lc14-num-failrate}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc14-num-pass-to-fail}\\
\multirow{2}{*}{\parbox{8cm}{LC10: \UseMacro{test-results-hs-lc15}}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc15-num-tcs}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc15-num-seeds}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc15-num-exps}}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc15-num-all-fail}/\UseMacro{test-results-hs-bl-model0-lc15-num-fail}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc15-num-all-failrate}/\UseMacro{test-results-hs-bl-model0-lc15-num-failrate}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc15-num-pass-to-fail}\\
 & & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc15-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc15-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc15-num-all-failrate}/\UseMacro{test-results-hs-bl-model1-lc15-num-failrate}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc15-num-pass-to-fail}\\
\multirow{2}{*}{\parbox{8cm}{LC11: \UseMacro{test-results-hs-lc16}}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc16-num-tcs}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc16-num-seeds}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc16-num-exps}}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc16-num-all-fail}/\UseMacro{test-results-hs-bl-model0-lc16-num-fail}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc16-num-all-failrate}/\UseMacro{test-results-hs-bl-model0-lc16-num-failrate}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc16-num-pass-to-fail}\\
 & & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc16-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc16-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc16-num-all-failrate}/\UseMacro{test-results-hs-bl-model1-lc16-num-failrate}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc16-num-pass-to-fail}\\
\multirow{2}{*}{\parbox{8cm}{LC12: \UseMacro{test-results-hs-lc17}}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc17-num-tcs}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc17-num-seeds}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc17-num-exps}}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc17-num-all-fail}/\UseMacro{test-results-hs-bl-model0-lc17-num-fail}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc17-num-all-failrate}/\UseMacro{test-results-hs-bl-model0-lc17-num-failrate}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc17-num-pass-to-fail}\\
 & & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc17-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc17-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc17-num-all-failrate}/\UseMacro{test-results-hs-bl-model1-lc17-num-failrate}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc17-num-pass-to-fail}\\
\multirow{2}{*}{\parbox{8cm}{LC13: \UseMacro{test-results-hs-lc18}}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc18-num-tcs}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc18-num-seeds}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc18-num-exps}}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc18-num-all-fail}/\UseMacro{test-results-hs-bl-model0-lc18-num-fail}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc18-num-all-failrate}/\UseMacro{test-results-hs-bl-model0-lc18-num-failrate}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc18-num-pass-to-fail}\\
 & & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc18-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc18-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc18-num-all-failrate}/\UseMacro{test-results-hs-bl-model1-lc18-num-failrate}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc18-num-pass-to-fail}\\
\multirow{2}{*}{\parbox{8cm}{LC14: \UseMacro{test-results-hs-lc19}}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc19-num-tcs}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc19-num-seeds}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc19-num-exps}}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc19-num-all-fail}/\UseMacro{test-results-hs-bl-model0-lc19-num-fail}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc19-num-all-failrate}/\UseMacro{test-results-hs-bl-model0-lc19-num-failrate}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc19-num-pass-to-fail}\\
 & & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc19-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc19-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc19-num-all-failrate}/\UseMacro{test-results-hs-bl-model1-lc19-num-failrate}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc19-num-pass-to-fail}\\

>>>>

\resizebox{0.8\textwidth}{!}{

@@

\multirow{2}{*}{\parbox{8cm}{LC1: \UseMacro{test-results-hs-lc0}}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc0-num-tcs}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc0-num-seeds}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc0-num-exps}}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc0-num-all-fail}/\UseMacro{test-results-hs-bl-model0-lc0-num-fail}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc0-num-all-failrate}/\UseMacro{test-results-hs-bl-model0-lc0-num-failrate}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc0-num-pass-to-fail}\\
 & & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc0-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc0-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc0-num-all-failrate}/\UseMacro{test-results-hs-bl-model1-lc0-num-failrate}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc0-num-pass-to-fail}\\
\multirow{2}{*}{\parbox{8cm}{LC2: \UseMacro{test-results-hs-lc1}}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc1-num-tcs}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc1-num-seeds}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc1-num-exps}}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc1-num-all-fail}/\UseMacro{test-results-hs-bl-model0-lc1-num-fail}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc1-num-all-failrate}/\UseMacro{test-results-hs-bl-model0-lc1-num-failrate}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc1-num-pass-to-fail}\\
 & & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc1-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc1-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc1-num-all-failrate}/\UseMacro{test-results-hs-bl-model1-lc1-num-failrate}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc1-num-pass-to-fail}\\
\multirow{2}{*}{\parbox{8cm}{LC3: \UseMacro{test-results-hs-lc2}}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc2-num-tcs}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc2-num-seeds}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc2-num-exps}}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc2-num-all-fail}/\UseMacro{test-results-hs-bl-model0-lc2-num-fail}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc2-num-all-failrate}/\UseMacro{test-results-hs-bl-model0-lc2-num-failrate}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc2-num-pass-to-fail}\\
 & & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc2-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc2-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc2-num-all-failrate}/\UseMacro{test-results-hs-bl-model1-lc2-num-failrate}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc2-num-pass-to-fail}\\
\multirow{2}{*}{\parbox{8cm}{LC4: \UseMacro{test-results-hs-lc3}}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc3-num-tcs}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc3-num-seeds}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc3-num-exps}}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc3-num-all-fail}/\UseMacro{test-results-hs-bl-model0-lc3-num-fail}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc3-num-all-failrate}/\UseMacro{test-results-hs-bl-model0-lc3-num-failrate}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc3-num-pass-to-fail}\\
 & & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc3-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc3-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc3-num-all-failrate}/\UseMacro{test-results-hs-bl-model1-lc3-num-failrate}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc3-num-pass-to-fail}\\
\multirow{2}{*}{\parbox{8cm}{LC5: \UseMacro{test-results-hs-lc4}}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc4-num-tcs}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc4-num-seeds}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc4-num-exps}}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc4-num-all-fail}/\UseMacro{test-results-hs-bl-model0-lc4-num-fail}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc4-num-all-failrate}/\UseMacro{test-results-hs-bl-model0-lc4-num-failrate}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc4-num-pass-to-fail}\\
 & & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc4-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc4-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc4-num-all-failrate}/\UseMacro{test-results-hs-bl-model1-lc4-num-failrate}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc4-num-pass-to-fail}\\
\multirow{2}{*}{\parbox{8cm}{LC6: \UseMacro{test-results-hs-lc5}}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc5-num-tcs}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc5-num-seeds}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc5-num-exps}}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc5-num-all-fail}/\UseMacro{test-results-hs-bl-model0-lc5-num-fail}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc5-num-all-failrate}/\UseMacro{test-results-hs-bl-model0-lc5-num-failrate}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc5-num-pass-to-fail}\\
 & & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc5-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc5-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc5-num-all-failrate}/\UseMacro{test-results-hs-bl-model1-lc5-num-failrate}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc5-num-pass-to-fail}\\
\multirow{2}{*}{\parbox{8cm}{LC7: \UseMacro{test-results-hs-lc6}}}

@@

\multirow{2}{*}{\parbox{8cm}{LC8: \UseMacro{test-results-hs-lc7}}}

@@

\multirow{2}{*}{\parbox{8cm}{LC9: \UseMacro{test-results-hs-lc8}}}

@@

\multirow{2}{*}{\parbox{8cm}{LC10: \UseMacro{test-results-hs-lc9}}}

@@

\multirow{2}{*}{\parbox{8cm}{LC11: \UseMacro{test-results-hs-lc10}}}

@@

\multirow{2}{*}{\parbox{8cm}{LC12: \UseMacro{test-results-hs-lc11}}}

@@

\multirow{2}{*}{\parbox{8cm}{LC13: \UseMacro{test-results-hs-lc12}}}

@@

\multirow{2}{*}{\parbox{8cm}{LC14: \UseMacro{test-results-hs-lc13}}}

@@

### 2023-03-16 paper/icse24/threats.tex
icse24

There are two potential threats to validity.
First, the dataset
used in our study might not be representative of all
English grammatical structures and word sentiments. We
mitigate this threat by using widely used dataset in the NLP
domain~\cite{husnain2021swnvalidity}.
Second, using ranges of the sentiment scores in SST-2 to determine the sentiment labels of search dataset may introduce incorrect labels. We performed a manual study to confirm that this is rare. 
% Use of publicly available datasets poses an external validity threat
% with respect to the generalizability of our results. We implemented
% domain-specific knowledge on publicly available word sentiments
% dataset~\cite{baccianella2010sentiwordnet}. We also constructed
% reference CFG from publicly available corpus dataset
\cite{mitchell1993treebank, nltkTreebankCorporaWebPage}.

>>>>

There are two potential threats to validity.
First, the dataset
used in our study might not be representative of all
English grammatical structures and word sentiments. We
mitigate this threat by using widely used dataset in the NLP
domain~\cite{husnain2021swnvalidity}.
Second, using ranges of the sentiment scores in \Sst and majority voting 
method in \Hatexp to determine the sentiment labels of search dataset may 
introduce incorrect labels. We performed a manual study to confirm that 
this is rare. 
% Use of publicly available datasets poses an external validity threat
% with respect to the generalizability of our results. We implemented
% domain-specific knowledge on publicly available word sentiments
% dataset~\cite{baccianella2010sentiwordnet}. We also constructed
% reference CFG from publicly available corpus dataset
% \cite{mitchell1993treebank, nltkTreebankCorporaWebPage}.
